Preprocess

### 2024-01-25 src/preprocess.Rmd
Sanitized counts

# Get phy coded records only
out_coded <- out %>% filter(
    !is.na(physician_icd10) & !is.null(physician_icd10)
)
out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)

# Get chatgpt3 coded records
out_cgpt3 <- out_coded %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)
out_cgpt3_agree <- out_coded_agree %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)

# Get chatgpt3 coded records converted to cghr10
out_cgpt3_cghr10 <- out_cgpt3 %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)
out_cgpt3_cghr10_agree <- out_cgpt3_agree %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)

# Print results
cat(paste0(
    "ICD-10 Output\n-------------",
    "\nChatGPT-3.5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3 %>% nrow,
    "\nChatGPT-3.5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_agree %>% nrow,
    "\n\nAfter Conversion to CGHR-10\n---------------------------",
    "\nChatGPT-3.5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3_cghr10 %>% nrow,
    "\nChatGPT-3.5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_cghr10_agree %>% nrow
))
```

@@

# Get phy coded records only
out_coded <- out %>% filter(
    !is.na(physician_icd10) & !is.null(physician_icd10)
)
out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)

# Get chatgpt4 coded records
out_cgpt4 <- out_coded %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)
out_cgpt4_agree <- out_coded_agree %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)

# Get chatgpt4 coded records converted to cghr10
out_cgpt4_cghr10 <- out_cgpt4 %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)
out_cgpt4_cghr10_agree <- out_cgpt4_agree %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)

# Print results
cat(paste0(
    "ICD-10 Output\n-------------",
    "\nChatGPT-4 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4 %>% nrow,
    "\nChatGPT-4 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_agree %>% nrow,
    "\n\nAfter Conversion to CGHR-10\n---------------------------",
    "\nChatGPT-4 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4_cghr10 %>% nrow,
    "\nChatGPT-4 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_cghr10_agree %>% nrow
))
```

@@

# Get interva5 coded records in wva2016
out_iva5 <- out_who %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_agree <- out_who_agree %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)

# Get interva5 wva2016 coded records converted to icd10
out_iva5_icd10 <- out_iva5 %>% filter(
    !is.na(interva5_icd10) & !is.null(interva5_icd10)
)
out_iva5_icd10_agree <- out_iva5_agree %>% filter(
    !is.na(interva5_icd10) & !is.null(interva5_icd10)
)

# Get interva5 icd10 coded records converted to cghr10
out_iva5_cghr10 <- out_iva5_icd10 %>% filter(
    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
)
out_iva5_cghr10_agree <- out_iva5_icd10_agree %>% filter(
    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
)

# Print results
cat(paste0(
    "InterVA-5 WVA-2016 Output\n-------------------------",
    "\nInterVA-5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_iva5 %>% nrow,
    "\nInterVA-5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_agree %>% nrow,
    "\n\nAfter Conversion from WVA-2016 to ICD-10\n----------------------------------------",
    "\nInterVA-5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_iva5_icd10 %>% nrow,
    "\nInterVA-5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_icd10_agree %>% nrow,
    "\n\nAfter Conversion from ICD-10 to CGHR-10\n---------------------------------------",
    "\nInterVA-5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_iva5_cghr10 %>% nrow,
    "\nInterVA-5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_cghr10_agree %>% nrow
))
```

@@

# Get who
out_who <- out %>% left_join(
    df$who %>% mutate(rowid_who = rowid),
    by = c("rowid" = "rowid"),
    suffix = c("", "")
) %>% filter(!is.na(rowid_who) & !is.na(physician_icd10))
out_who_agree <- out_who %>% filter(is_agreed == TRUE)

# Get insilicova coded records in wva2016
out_isva <- out_who %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_agree <- out_who_agree %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)

# Get insilicova wva2016 coded records converted to icd10
out_isva_icd10 <- out_isva %>% filter(
    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
)
out_isva_icd10_agree <- out_isva_agree %>% filter(
    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
)

# Get insilicova icd10 coded records converted to cghr10
out_isva_cghr10 <- out_isva_icd10 %>% filter(
    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
)
out_isva_cghr10_agree <- out_isva_icd10_agree %>% filter(
    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
)

# Print results
cat(paste0(
    "InSilicoVA WVA-2016 Output\n-------------------------",
    "\nInSilicoVA ICD-10 Coded (Phy. ICD-10 Coded): ", out_isva %>% nrow,
    "\nInSilicoVA ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_agree %>% nrow,
    "\n\nAfter Conversion from WVA-2016 to ICD-10\n----------------------------------------",
    "\nInSilicoVA ICD-10 Coded (Phy. ICD-10 Coded): ", out_isva_icd10 %>% nrow,
    "\nInSilicoVA ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_icd10_agree %>% nrow,
    "\n\nAfter Conversion from ICD-10 to CGHR-10\n---------------------------------------",
    "\nInSilicoVA CGHR-10 Coded (Phy. ICD-10 Coded): ", out_isva_cghr10 %>% nrow,
    "\nInSilicoVA CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_cghr10_agree %>% nrow
))
```

>>>>

# Get phy coded icd10 records only
out_coded <- out %>% filter(
    !is.na(physician_icd10) & !is.null(physician_icd10)
)
out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)

# Get phy coded cghr10 records only
out_coded_cghr10 <- out_coded %>% filter(
    !is.na(physician_cghr10) & !is.null(physician_cghr10)
)
out_coded_cghr10_agree <- out_coded_cghr10 %>% filter(is_agreed == TRUE)

# Get chatgpt3 coded records
out_cgpt3 <- out_coded %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)
out_cgpt3_agree <- out_coded_agree %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)
out_cgpt3_cghr10 <- out_coded_cghr10 %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)
out_cgpt3_cghr10_agree <- out_coded_cghr10_agree %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)

# Get chatgpt3 coded records converted to cghr10
out_cgpt3_xcghr10 <- out_cgpt3 %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)
out_cgpt3_xcghr10_agree <- out_cgpt3_agree %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)
out_cgpt3_xcghr10_cghr10 <- out_cgpt3_cghr10 %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)
out_cgpt3_xcghr10_cghr10_agree <- out_cgpt3_cghr10_agree %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)

# Print results
cat(paste0(
    "ICD-10 Output\n-------------",
    "\nChatGPT-3.5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3 %>% nrow,
    "\nChatGPT-3.5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_agree %>% nrow,
    "\nChatGPT-3.5 ICD-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt3_cghr10 %>% nrow,
    "\nChatGPT-3.5 ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt3_cghr10_agree %>% nrow,
    "\n\nAfter Conversion to CGHR-10\n---------------------------",
    "\nChatGPT-3.5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt3_xcghr10 %>% nrow,
    "\nChatGPT-3.5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt3_xcghr10_agree %>% nrow,
    "\nChatGPT-3.5 CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt3_xcghr10_cghr10 %>% nrow,
    "\nChatGPT-3.5 CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt3_xcghr10_cghr10_agree %>% nrow
))
```

@@

# Get phy coded icd10 records only
out_coded <- out %>% filter(
    !is.na(physician_icd10) & !is.null(physician_icd10)
)
out_coded_agree <- out_coded %>% filter(is_agreed == TRUE)

# Get phy coded cghr10 records only
out_coded_cghr10 <- out_coded %>% filter(
    !is.na(physician_cghr10) & !is.null(physician_cghr10)
)
out_coded_cghr10_agree <- out_coded_cghr10 %>% filter(is_agreed == TRUE)

# Get chatgpt4 coded records
out_cgpt4 <- out_coded %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)
out_cgpt4_agree <- out_coded_agree %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)
out_cgpt4_cghr10 <- out_coded_cghr10 %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)
out_cgpt4_cghr10_agree <- out_coded_cghr10_agree %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)

# Get chatgpt4 coded records converted to cghr10
out_cgpt4_xcghr10 <- out_cgpt4 %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)
out_cgpt4_xcghr10_agree <- out_cgpt4_agree %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)
out_cgpt4_xcghr10_cghr10 <- out_cgpt4_cghr10 %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)
out_cgpt4_xcghr10_cghr10_agree <- out_cgpt4_cghr10_agree %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)

# Print results
cat(paste0(
    "ICD-10 Output\n-------------",
    "\nChatGPT-4 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4 %>% nrow,
    "\nChatGPT-4 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_agree %>% nrow,
    "\nChatGPT-4 ICD-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt4_cghr10 %>% nrow,
    "\nChatGPT-4 ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt4_cghr10_agree %>% nrow,
    "\n\nAfter Conversion to CGHR-10\n---------------------------",
    "\nChatGPT-4 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt4_xcghr10 %>% nrow,
    "\nChatGPT-4 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt4_xcghr10_agree %>% nrow,
    "\nChatGPT-4 CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt4_xcghr10_cghr10 %>% nrow,
    "\nChatGPT-4 CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt4_xcghr10_cghr10_agree %>% nrow
))
```

@@

# Get who with physician coded records converted to CGHR-10
out_who_cghr10 <- out %>% filter(!is.na(physician_cghr10))
out_who_cghr10_agree <- out_who_cghr10 %>% filter(is_agreed == TRUE)

# Get interva5 coded records in wva2016
out_iva5 <- out_who %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_agree <- out_who_agree %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_cghr10 <- out_who_cghr10 %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_chr10_agree <- out_who_cghr10_agree %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)

# Get interva5 wva2016 coded records converted to icd10
out_iva5_icd10 <- out_iva5 %>% filter(
    !is.na(interva5_icd10) & !is.null(interva5_icd10)
)
out_iva5_icd10_agree <- out_iva5_agree %>% filter(
    !is.na(interva5_icd10) & !is.null(interva5_icd10)
)
out_iva5_icd10_cghr10 <- out_iva5_cghr10 %>% filter(
    !is.na(interva5_icd10) & !is.null(interva5_icd10)
)
out_iva5_icd10_cghr10_agree <- out_iva5_cghr10_agree %>% filter(
    !is.na(interva5_icd10) & !is.null(interva5_icd10)
)

# Get interva5 icd10 coded records converted to cghr10
out_iva5_xcghr10 <- out_iva5_icd10 %>% filter(
    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
)
out_iva5_xcghr10_agree <- out_iva5_icd10_agree %>% filter(
    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
)
out_iva5_xcghr10_cghr10 <- out_iva5_icd10_cghr10 %>% filter(
    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
)
out_iva5_xcghr10_cghr10_agree <- out_iva5_icd10_cghr10_agree %>% filter(
    !is.na(interva5_cghr10) & !is.null(interva5_cghr10)
)

# Print results
cat(paste0(
    "InterVA-5 WVA-2016 Output\n-------------------------",
    "\nInterVA-5 WVA-2016 Coded (Phy. ICD-10 Coded): ", out_iva5 %>% nrow,
    "\nInterVA-5 WVA-2016 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_agree %>% nrow,
    "\nInterVA-5 WVA-2016 Coded (Phy. CGHR-10 Coded): ", out_iva5_cghr10 %>% nrow,
    "\nInterVA-5 WVA-2016 Coded (Agree, Phy. CGHR-10 Coded): ", out_iva5_cghr10_agree %>% nrow,
    "\n\nAfter Conversion from WVA-2016 to ICD-10\n----------------------------------------",
    "\nInterVA-5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_iva5_icd10 %>% nrow,
    "\nInterVA-5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_icd10_agree %>% nrow,
    "\nInterVA-5 ICD-10 Coded (Phy. CGHR-10 Coded): ", out_iva5_icd10_cghr10 %>% nrow,
    "\nInterVA-5 ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_iva5_icd10_cghr10_agree %>% nrow,
    "\n\nAfter Conversion from ICD-10 to CGHR-10\n---------------------------------------",
    "\nInterVA-5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_iva5_xcghr10 %>% nrow,
    "\nInterVA-5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_iva5_xcghr10_agree %>% nrow,
    "\nInterVA-5 CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_iva5_xcghr10_cghr10 %>% nrow,
    "\nInterVA-5 CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_iva5_xcghr10_cghr10_agree %>% nrow
))
```

@@

# Get who with physician coded records converted to CGHR-10
out_who_cghr10 <- out %>% filter(!is.na(physician_cghr10))
out_who_cghr10_agree <- out_who_cghr10 %>% filter(is_agreed == TRUE)

# Get insilicova coded records in wva2016
out_isva <- out_who %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_agree <- out_who_agree %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_cghr10 <- out_who_cghr10 %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_chr10_agree <- out_who_cghr10_agree %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)

# Get insilicova wva2016 coded records converted to icd10
out_isva_icd10 <- out_isva %>% filter(
    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
)
out_isva_icd10_agree <- out_isva_agree %>% filter(
    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
)
out_isva_icd10_cghr10 <- out_isva_cghr10 %>% filter(
    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
)
out_isva_icd10_cghr10_agree <- out_isva_cghr10_agree %>% filter(
    !is.na(insilicova_icd10) & !is.null(insilicova_icd10)
)

# Get insilicova icd10 coded records converted to cghr10
out_isva_xcghr10 <- out_isva_icd10 %>% filter(
    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
)
out_isva_xcghr10_agree <- out_isva_icd10_agree %>% filter(
    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
)
out_isva_xcghr10_cghr10 <- out_isva_icd10_cghr10 %>% filter(
    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
)
out_isva_xcghr10_cghr10_agree <- out_isva_icd10_cghr10_agree %>% filter(
    !is.na(insilicova_cghr10) & !is.null(insilicova_cghr10)
)

# Print results
cat(paste0(
    "InSilicoVA WVA-2016 Output\n-------------------------",
    "\nInSilicoVA WVA-2016 Coded (Phy. ICD-10 Coded): ", out_isva %>% nrow,
    "\nInSilicoVA WVA-2016 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_agree %>% nrow,
    "\nInSilicoVA WVA-2016 Coded (Phy. CGHR-10 Coded): ", out_isva_cghr10 %>% nrow,
    "\nInSilicoVA WVA-2016 Coded (Agree, Phy. CGHR-10 Coded): ", out_isva_cghr10_agree %>% nrow,
    "\n\nAfter Conversion from WVA-2016 to ICD-10\n----------------------------------------",
    "\nInSilicoVA ICD-10 Coded (Phy. ICD-10 Coded): ", out_isva_icd10 %>% nrow,
    "\nInSilicoVA ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_icd10_agree %>% nrow,
    "\nInSilicoVA ICD-10 Coded (Phy. CGHR-10 Coded): ", out_isva_icd10_cghr10 %>% nrow,
    "\nInSilicoVA ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_isva_icd10_cghr10_agree %>% nrow,
    "\n\nAfter Conversion from ICD-10 to CGHR-10\n---------------------------------------",
    "\nInSilicoVA CGHR-10 Coded (Phy. ICD-10 Coded): ", out_isva_xcghr10 %>% nrow,
    "\nInSilicoVA CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_isva_xcghr10_agree %>% nrow,
    "\nInSilicoVA CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_isva_xcghr10_cghr10 %>% nrow,
    "\nInSilicoVA CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_isva_xcghr10_cghr10_agree %>% nrow
))
```
